---
title: "Stat 440 Project Proposal"
author: 'Group B: Matthew Bayley , Oki Ogbe, Sabrina Pribyl'
date: "4/12/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data  
The data set we will be using is the Burrito ratings data. This data set contains ratings of about 200 burritos in San Diego from roughly 50 restaurants. The burritos are rated based off of 10 different aspects of the burrito where each is on a scale of 1 to 5.  
```{r}
#load(file="Burrito/burritodata.Rda")
load("/cloud/project/burritodata.Rda")
```

## Research Question
A classic San Diego burrito ingredient (so we're told) is potatoes. We will be testing if fries significantly increase the overall rating of a burrito. 

Model 1:
- Indicator: potato
- random effect: reviewer, he suggested not using restaurant as a random effect

Y = Overall rating 
$X_{1}$= Potatoes
$X_{2}$ = Reviewer

Model 2:
- Control for common ingredients, maybe certain types of meat are common to pair with potatoes (confounding - associated with potatoes and the outcome)

Y = Overall rating
$X_{1}$ = Potatoes
$X_{2}$ = Beef
$X_{3}$ = Cheese
$X_{4}$ = Guac
$X_{5}$ = Pico


$$Y|\beta, \sigma^{-2} \sim MVN(\textbf{X}\beta,\sigma^{-2}\textbf{I})$$

$$\beta \sim MVN(\mu,\tau^{2}\textbf{I})$$
```{r, include=FALSE}

mu = mean(burrito$overall, na.rm = T)
tau2 = var(burrito$overall, na.rm = T)
```

$$\mu = 3.537$$

$$\tau^{2} = 0.681$$

$$\sigma^{-2} \sim Gamma(a,b)$$



a = .1
b = .1








## Exploratory Analysis
```{r}
## Distribution of reviewers 
library(ggplot2)
ggplot(data.frame(burrito$Reviewer), aes(x=burrito$Reviewer)) +
  geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("Distribution Reviewers") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Reviewer") + ylab("Number of Reviews") 

factorBurrito <- as.factor(burrito$Reviewer)
levels(factorBurrito) #71 reviewers

table(burrito$Reviewer) #many reviewers only appear once

countG1 = 0
countG5 = 0
for(i in 1:length(table(burrito$Reviewer))){
  if(table(burrito$Reviewer)[i] > 1){
    countG1 <- countG1 + 1
    if(table(burrito$Reviewer)[i] > 5){
      countG5 <- countG5 + 1
      table(burrito$Reviewer)[i]
    }
  }else{
  }
}
countG1 ## only 20 reviewers reviewed more than 1 burrito
countG5 ## only 6 reviewers reviewed more than 5 burritos

##############
## Potato Data
##############

library(plyr)
count(burrito$Fries == 1)

## Potatoes
potatoData <- burrito[which(burrito$Fries == "1"),]
potatoData <- potatoData[complete.cases(potatoData), ]
factorBurrito2 <- as.factor(potatoData$Reviewer)
levels(factorBurrito2) #Only 32 reviewers reviewed burritos with potatoes 

## Distribution of reviewers rating burritos with potatoes
ggplot(data.frame(potatoData$Reviewer), aes(x=potatoData$Reviewer)) +
  geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("Distribution Reviewers Rating Burritos With Potatoes") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Reviewer") + ylab("Number of Reviews") 



p <- ggplot(data.frame(Ingredient=ingredients, Proportion=colMeans(potatoData[,ingredients]))) + geom_point(aes(x=Ingredient, y=Proportion, colour = Proportion>.4)) + 
  ggtitle("Common Ingredients With Potatoes") + 
  theme(plot.title = element_text(hjust = 0.5)) 
p <- p +  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1))
p <- p + ylim(0,1)
print(p) ## Common ingredients with potatoes: Beef, Cheese, Guac, Pico, Sour Cream (Possibly Sauce)


## Distribution of Reviews
Mean <- mean(burrito$overall)
burrito$overall

ggplot(data.frame(burrito$overall), aes(x=burrito$overall)) +
  geom_bar() + ggtitle("Distribution of Overall Rating") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Overall Rating") + ylab("Count") +
  geom_vline(xintercept = MeanPotato, col = 2)

## Distribution of Reviews for burritos with Potatoes 
MeanPotato <- mean(potatoData$overall)
MeanPotato

ggplot(data.frame(potatoData$overall), aes(x=potatoData$overall)) +
  geom_bar() + xlim(1, 5) + ggtitle("Distribution of Overall Rating for Burritos with Potatoes") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Overall Rating") + ylab("Count") +
  geom_vline(xintercept = MeanPotato, col = 2)


```

## Cleaning our data
To start, we removed unnecessary variables for our analysis which included location, cost, hunger, length, circumference, volume, and all of the rating variables besides overall rating. We also cleaned our data to get rid of any NAs. We are left with the variables reviewer and the 33 ingredients. 